Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-12-01 files/Overview.tex
chapter 4 and overview update
Chapter 3 final
Overview

\subsubsection{Chapter 3}
In this chapter, some theory for the Finite Element Method is discussed. This chapter contains two parts, that covers two different theoretical results. The first is on the convergence of the Galerkin approximation of a general vibration problem. This theory is presented in the article \cite{BV13}. The second part concerns the convergence of the eigenvalues and eigenfunctions of a vibration problem when applying the Finite Element Method. This theory is presented in the textbook \cite{SF73}\textcolor{red}{Nie goed genoeg vir dinamiese probleem}.

@@

\textcolor{red}{*************Copy van chapter 6******************}

The first section is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.

\textcolor{red}{*******************************}

@@

\textcolor{red}{*************hou voorlopig******************}

The first section is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.

\textcolor{red}{*******************************}

>>>>

\subsubsection{Chapter 3}
In this chapter, some theory for the Finite Element Method is discussed. This chapter contains two parts, that covers two different theoretical results. The first is on the convergence of the Galerkin approximation of a general vibration problem. This theory is presented in the article \cite{BV13}. The second part concerns the convergence of the eigenvalues and eigenfunctions of a vibration problem when applying the Finite Element Method. This theory is presented in the textbook \cite{SF73}.

@@

Section 4.5 is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions. (See Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. \textcolor{red}{The results show that the shape of the beam impacts the comparison. The comparison improves as the beam gets more slender, but overall the comparisons are very good.}\sout{As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.}

@@

\sout{The first section is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of a cantilever Timoshenko beam model, by comparing it to a two-dimensional cantilever Timoshenko beam model. The authors compare the models by comparing the eigenvalues and eigenfunctions (see Chapter 2 on modal analysis). The two-dimensional model is more complex and there are eigenvalues that are not shared between the models. The authors use the mode shapes to match up the eigenvalues. The eigenvalues matching the eigenvalues of the Timoshenko beam model are referred to by the authors as beam-type eigenvalues. The authors also consider different shapes of beams, from a short thick beam to a long slender beam. The results show that the models compare very well, even for a short and thick beam. As the beam gets more slender, the comparison improves. In this section some of the results of the article are discussed and replicated.}
